Predicting the conformational preferences of proteins using a physics-based free energy method

### 2013-05-08 Paper/paper.tex
May8th

One advantage of confinement method is that
none of the simulations during the restraining step depends on each other. Therefore, with available computer resources it can be fast 
to compute. The computational cost of a single 20 ns simulation (along the confinement step) of $56$-residue protein 
is only $4$ hours in a single gpu computer  \Alberto{all the different confinements in one GPU?}. All calculations were
performed with the Amber 11 suit of programs~\cite{Case2012,Goetz2012} in combination with the ff99SB
forcefield~\cite{Hornak2006} and the generalized born implicit solvent \cite{Mongan2006}.

>>>>

One advantage of confinement method is that
none of the simulations during the restraining step depends on each other. Therefore, with available computer resources it can be fast 
to compute. The computational cost for a single 20 ns simulation (along the confinement step) of $56$-residue protein 
is only $4$ hours in a single gpu computer  \Alberto{all the different confinements in one GPU?}. All calculations were
performed with the Amber 11 suit of programs~\cite{Case2012,Goetz2012} in combination with the ff99SB
forcefield~\cite{Hornak2006} and the generalized born implicit solvent \cite{Mongan2006}.
